Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-20 article/article.tex
(+) Par on grouping results

The traffic is simulated the following way, each elementary module has an
associted list which, at index \(i\) has the number of aircraft in it at time
step \(i\). Those lists have been written by hand, the activity shows a traffic
peak at the beginning of the scenario and much less activity after. The expected
outcome of the algorithms is a massive degrouping reflecting the heavy workload
followed by merges.

@@

The graph~\ref{fig:grouping} asserts the correct behaviour of both algorithms
A\(^*\) and MCTS regarding grouping and degrouping. On the \(y\) axis is
indicated the number of sectors. The two algorithms show, as expected, splits
leading from 3 sectors to 5 for the MCTS to cope with the intense trafic at
the beginning of the scenario. Both algorithm choose to merge as much as
possible to go to 1 sector.

\begin{table}
  \centering
  \begin{tabulary}
    {\textwidth}{LRR}
    Alg. & Cost & Err.\\\toprule
    A\(^*\) & 77.31 & 0\%    \\
    MCTS    & 82.48 & 6.7\%  \\
    Greedy  & 90.50 & 17.1\% \\
  \end{tabulary}
  \caption{Comparison of several methods on the generated
  scenario.}\label{tab:methods_compare}
\end{table}

>>>>

The traffic is simulated the following way, each elementary module has an
associted list which, at index \(i\) has the number of aircraft in it at time
step \(i\). Those lists have been written by hand.

@@

The graph~\ref{fig:grouping} asserts the correct behaviour of both algorithms
A\(^*\) and MCTS regarding grouping and degrouping. On the \(y\) axis is
indicated the number of sectors. The trafic activity is the following,
\begin{enumerate}
  \item\label{scen:busy}
    The first part of the scenario shows a busy situation, all sectors are
    overloaded;
  \item\label{scen:quiet}
    then follows a quiet moment with few aircraft, much of the sectors are
    underloaded;
  \item\label{scen:partial}
    the end of the scenario has two overload modules and the rest under
    normal or under load.
\end{enumerate}
The expected behaviour is a tendency to increase the number of sectors through
splits to cope with part~\ref{scen:busy} followed by many merges to reduce the
number of sectors in response to phase~\ref{scen:quiet}. The algorithms should
end with a specific sector created, the one overloaded in~\ref{scen:partial} and
the rest grouped. Seeing~\ref{fig:grouping}, both algorithm behave as expected.
\begin{table}
  \centering
  \begin{tabulary}
    {\textwidth}{LRR}
    Alg. & Cost & Err.\\\toprule
    A\(^*\) & 77.31 & 0\%    \\
    MCTS    & 82.48 & 6.7\%  \\
    Greedy  & 90.50 & 17.1\% \\
  \end{tabulary}
  \caption{Comparison of several methods on the generated
  scenario.}\label{tab:methods_compare}
\end{table}
